Open-source landscape for 3D CSEM modelling

### 2020-10-09 manuscript/Manuscript.tex

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}

The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model. At, e.g., two kilometers below the seafloor there are already significant changes visible, purely due to meshing. This is an important insight that has to be taken into account when interpreting inversion results.

@@

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use?}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use?}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 & 3527 & 437.8 & 4539474 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}

>>>>

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain. (Vertical exaggeration: 5.45)}

The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model. At, e.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing. This is an important insight that has to be taken into account when interpreting inversion results.

@@

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use? (Vertical exaggeration: 1.33)}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use? (Vertical exaggeration: 4.0)}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 &  524 & 175.4 & 1918106 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}
